Theoretical aspects in gravity modelling

### 2018-04-27 manuscript/letter.tex
Updating article

The gravity anomaly is the commonly used quantity in applied 
geophysics. At point $P$, it is defined as the difference between the 
gravity vector at a point $Q^{\prime}$ on the Geoid (a particular 
equipotential surface of the gravity potential) and the normal gravity 
vector at a point $Q$ on the ellipsoid surface, both at the same
geodetic latitude and longitude (Fig. \ref{fig:surfaces}) as in
\begin{equation}
\Delta \mitbf{g}_{P} = \mitbf{g}_{Q^{\prime}} - \mitbf{\gamma}_{Q} .
\label{eq:gravity-anomaly-vector}
\end{equation}
Similarly to the gravity disturbance expression (eq.
\ref{eq:gravity-disturbance}), the gravity anomaly is given by
\begin{equation}
\Delta g_{P} = g_{Q^{\prime}} - \gamma_{Q} ,
\label{eq:gravity-anomaly}
\end{equation}
where $g_{Q^{\prime} } = \| \mitbf{g}_{Q^{\prime}} \|$ is
the magnitude of the gravity vector $\mitbf{g}_{Q}$ at $Q^{\prime}$, 
on the Geoid, and $\gamma_{Q} = \| \mitbf{\gamma}_{Q} \|$ is the 
magnitude of the normal gravity vector $\mitbf{\gamma}_{Q}$ at $Q$, 
on the reference ellipsoid (Fig. \ref{fig:surfaces}).
Notice that, by definition, the gravity anomaly depends on 
longitude and latitude only and is not a function of height 
\citep{barthelmes2013}. As a consequence, it is not possible to compute,
for example, the upward continuation of a gravity anomaly.
However, many authors in the literature have computed the upward 
continuation of gravity anomalies. All these authors have
implicitly considered that the gravity anomaly is an approximation of 
the gravity disturbance, which in turn can be represented by a 
harmonic function that is allowed to be upward continued.

@@

\item Almost all interpretation techniques assume, implicitly or
directly, that the gravity data is harmonic (e.g., 
upward/downward continuation, 
data processing with equivalent layer,
conversions between gravity and magnetic data,
computation of vertical derivatives via Fourier and Hilbert
transforms). As a consequence, they implicitly or directly assume that
the gravity data approximate the gravitational disturbance.

\item Almost all forward modelling techniques compute
the vertical component of the gravitational attraction 
exerted by the gravity sources at the observation points.
Notice that the gravity anomaly requires the computation of gravity
on the Geoid, which is generally within the topographic masses.
Hence, almost all forward modelling techniques compute 
the gravity disturbance.

>>>>

Another anomalous quantity is the \textit{gravity anomaly vector}.
It is defined, at point $P$, as the difference between the gravity
vector at a point $Q^{\prime}$ on the Geoid (a particular
equipotential surface of the gravity potential) and the normal
gravity vector at a point $Q$ on the ellipsoid surface, both at the
same geodetic latitude and longitude (Fig. \ref{fig:surfaces}) as in
\begin{equation}
\Delta \mitbf{g}_{P} = \mitbf{g}_{Q^{\prime}} - \mitbf{\gamma}_{Q} .
\label{eq:gravity-anomaly-vector}
\end{equation}
Similarly to the gravity disturbance expression (eq.
\ref{eq:gravity-disturbance}), the gravity anomaly is given by
\begin{equation}
\Delta g_{P} = g_{Q^{\prime}} - \gamma_{Q} ,
\label{eq:gravity-anomaly}
\end{equation}
where $g_{Q^{\prime} } = \| \mitbf{g}_{Q^{\prime}} \|$ is
the magnitude of the gravity vector $\mitbf{g}_{Q}$ at $Q^{\prime}$, 
on the Geoid, and $\gamma_{Q} = \| \mitbf{\gamma}_{Q} \|$ is the 
magnitude of the normal gravity vector $\mitbf{\gamma}_{Q}$ at $Q$, 
on the reference ellipsoid (Fig. \ref{fig:surfaces}).
Notice that, by definition, the gravity anomaly depends on 
longitude and latitude only and is not a function of height 
\citep{barthelmes2013}. As a consequence, it is not possible to compute,
for example, the upward continuation of a gravity anomaly.
However, many authors in the literature have computed the upward 
continuation of gravity anomalies. All these authors have
implicitly considered that the gravity anomaly is an approximation of 
the gravity disturbance, which in turn can be represented by a 
harmonic function that is allowed to be upward continued.

@@

\item Almost all interpretation techniques assume, implicitly or
directly, that the gravity data is harmonic (e.g., 
upward/downward continuation, 
data processing with equivalent layer,
conversions between gravity and magnetic data,
computation of vertical derivatives via Fourier and Hilbert
transforms). As a consequence, they implicitly or directly assume that
the gravity data approximate the gravity disturbance.

\item Almost all forward modelling techniques compute
the vertical component of the gravitational attraction 
exerted by the gravity sources at the observation points.
Notice that the gravity anomaly requires the computation of gravity
on the Geoid, which is generally within the topographic masses.
Hence, almost all these forward modelling techniques in fact
compute the gravity disturbance.
